An agent-based model of local food systems

### 2016-05-13 draft.tex
update

To that end, we appreciate more realism than social scientists normally do. Following \textcite{Miller2009}, we attempt to model realistic ``in-between'' situations. For instance, agents are neither perfectly rational nor completely ignorant; the number of agents are neither a few nor infinite; and space and time are neither absent nor unbounded. Clearly, this is not how traditional analytical models are constructed, and cause and effect is less apparent than in closed-form equations. In order to make the internal mechanics transparent as well as flexible and extendable, we write codes in Python building upon Mesa \parencite{Mesa2016}, an open-source ABM framework. Our codes are also open-source and available on GitHub.com \parencite{Saikai2016}.

@@

\section{Local food systems}
(to be written)

\section{Agent-based modeling}
(to be written)

@@

\subsubsection{Social embeddedness $(e)$}
According to \textcite{Hinrichs2000}, the presence of social embeddedness is often seen as the hallmark of direct agricultural markets. At the same time, she also emphasizes an tension between embeddedness and marketness in each local food enterprise. Therefore, we introduce $e_j \in [0,1]$ capturing the embeddedness of the $j$th producer's enterprise. We interpret embeddedness as an objective property that reflects the socialness of the enterprise. In this way, it is distinguished from trust build upon the producer's personal characteristic. As a result, it enters into both objective functions, positive in utility and negative in profit, reflecting respectively consumer preference toward social experience in economic transaction and producers' customer maintenance costs.

>>>>

To that end, we appreciate more realism than social scientists normally do. Following \textcite{Miller2009}, we attempt to model realistic ``in-between'' scenarios. For instance, agents are neither perfectly rational nor completely ignorant; the number of agents is neither a few nor infinite; and space and time are neither absent nor unbounded. Clearly, this is not how traditional analytical models are constructed, and cause and effect are less apparent than in closed-form equations. In order to make the internal mechanics transparent as well as flexible and extendable, we write codes in Python building upon Mesa \parencite{Mesa2016}, an open-source ABM framework. Our codes are also open-source and available on GitHub.com \parencite{Saikai2016}.

@@

\section{Local food systems}
(literature review to be written)

\section{Agent-based modeling}
(literature review to be written)

@@

\subsubsection{Social embeddedness $(e)$}
According to \textcite{Hinrichs2000}, the presence of social embeddedness is often seen as the hallmark of direct agricultural markets. At the same time, she also emphasizes an tension between embeddedness and marketness in each local food enterprise. Therefore, we introduce $e_j \in [0,1]$ capturing the embeddedness of the $j$th producer's enterprise. We interpret embeddedness as an objective property that reflects the socialness of the enterprise. It is distinguished from trust, which is each consumer's subjective assessment of the `quality' of each producer. As a result, it enters into both objective functions, positive in utility and negative in profit, reflecting respectively consumer preference toward social experience in food transaction and producer's customer maintenance costs.
